Title: Fish do not need Visas: the transboundary nature of world fished species (70/96 character maximum)

### 2019-11-08 Manuscript_Draft.Rmd
Minor Changes

---
title: "Title: Fish do not need Visas: the transboundary nature of world fished species (70/96 character maximum )"
authors: "Authors: Juliano Palacios-Abrantes^1^, Gabriel Reygondeau^1^, William W.L. Cheung^1^"
date: "Affiliations: ^1^ Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada"
# subtitle: "Fish do not need Visas (16/40 character maximum)"
output:
  pdf_document:
    fig_caption: yes
  word_document:
    reference_docx: ./Manuscript_Instructions/science_template.docx
geometry: margin=1in
editor_options:
  chunk_output_type: console
bibliography: ./References/FishForVisa_Ref.bib
csl: ./References/science.csl
---

```{r setup, eval = T, echo=F, warning=F,message=F, results='hide'}

@@

#### Library ####
packages <- c(
  "dplyr", # Data manipulation
  "knitr",
  "kableExtra"
)

@@

Species are not randomly distributed in the world. The area in space and time where a stable population lives and reproduces is determined by the species' fitness response to a series of biotic and abiotic factors [@Hunch] and their influence in the evolutionary process [@REF]. Species distributions are key elements in marine resources management as human-made spatial boundaries are a major part of the management system [@Song:2017iua]. However, incorporating the concept of species distribution has not allays been the case in fisheries management, nor policy. The delimitation of Economic Exclusive Zones (EEZs) virtually splitted the distribution of many species, creating shared species between nations, and adding another level of complexity to fisheries management. However, 40 years after their establishment, the question of how many shared species exists in the world based on their distribution is still unanswered. In here, we show that many species are shared, representing an important contribution to national economies and food security, and highlighting the importance to acknowledge this in the policy arena.

@@

![**Number of transboundary species by EEZ and their production by country**](./Figures/Fig1.png)

@@

![**Number of transboundary and discrete species by country and continent**](./Figures/Fig2.png)

@@

![**Number of countries shared by transboundary species.** Showing only species that share > 20 countries](./Figures/Fig3.png)

>>>>

---
title: "Title: Fish do not need Visas: the transboundary nature of world fished species (70/96 character maximum)"
authors: "Authors: Juliano Palacios-Abrantes^1^, Gabriel Reygondeau^1,2^, William W.L. Cheung^1^"
date: "Affiliations: ^1^ Institute for the Oceans and Fisheries, University of British Columbia, Vancouver, Canada, ^2^ Yale"
# subtitle: "Fish do not need Visas (16/40 character maximum)"
output:
  pdf_document:
    fig_caption: yes
  word_document:
    reference_docx: ./Manuscript_Instructions/science_template.docx
geometry: margin=1in
editor_options:
  chunk_output_type: console
bibliography: ./References/FishForVisa_Ref.bib
csl: ./References/science.csl
---

```{r Ch2_setup, eval = T, echo=F, warning=F,message=F, results='hide'}

@@

#### Library ####
packages <- c(
  "dplyr", # Data manipulation
  "knitr",
  "kableExtra",
  "png",
  "grid",
  "here"

)

@@

Species are not randomly distributed in the world. The area in space and time where a stable population lives and reproduces is determined by the species' fitness response to a series of biotic and abiotic factors [@Hunch] and their influence in the evolutionary process [@REF]. Species distributions are key elements in marine resources management as human-made spatial boundaries are a major part of the management system [@Song:2017iua]. However, incorporating the concept of species distribution has not allays been the case in fisheries management, nor policy [@Alexa]. The delimitation of Economic Exclusive Zones (EEZs) in the arly 80's virtually splitted the distribution of many species, creating shared species between nations, and adding another level of complexity to fisheries management. However, 40 years after their establishment, the question of how many shared species exists in the world based on their distribution is still unanswered. In here, we take the most detailed database of marine fished species to show that many species are shared, representing an important contribution to national economies and food security, and highlighting the importance to acknowledge this in the policy arena.

@@

```{r Call_Map, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species by EEZ and their production by country"}

img <- readPNG(here("./Figures/Fig1.png"))
grid.raster(img)
```

@@

```{r Call_Country_Circular, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary and discrete species by country and continent"}

img <- readPNG(here("./Figures/Fig2.png"))
grid.raster(img)
```

@@

```{r Call_Spp_Circular, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Number of countries shared by transboundary species. Showing only species that share > 20 countries"}

img <- readPNG(here("./Figures/Fig3.png"))
grid.raster(img)
```
